\huge Tor's Usability for Censorship Circumvention

### 2016-04-18 pets2017-paper/pets2017-paper.tex
only keep total time table, commenting out active time table.
delete changes during experiment subsection

\subsection{Changes During the Experiment}

% $ grep 'default_bridge\.' tor-browser_en-US/Browser/TorBrowser/Data/Browser/profile.default/preferences/extension-overrides.js | awk -F. '{print $4}' | sort | uniq -c
%       5 flashproxy
%       6 fte
%       2 fte-ipv6
%       1 meek-amazon
%       1 meek-azure
%       1 meek-google
%       5 obfs3
%       3 obfs4
%       2 scramblesuit
% The 5 flashproxy lines are effectively 1.
Tor Browser 5.0.3 came configured with default bridges:
1 flashproxy;
8 fte;
3 meek;
5 obfs3;
3 obfs4;
and 2 scramblesuit.
In the time since 5.0.3 was released and our later experiment,
two of the obfs4 bridges and one of the scramblesuit bridges stopped running.
% These are the bridges that stopped running. schanenlied is known and intentional.
% 188.226.213.208 in known and intentional: https://bugs.torproject.org/17318. Maybe
% it was not even running at the time of 5.0.3.
% mercurius4 is probably not running by accident.
% schanenlied:
% obfs4 178.209.52.110:443 67E72FF33D7D41BF11C569646A0A7B4B188340DF cert=Z+cv8z19Qb8RxWlkagp7SxiDQN++b7D2Tntowhf+j4D15/kLuj3EoSSGvuREGPc3h60Ofw iat-mode=0
% mercurius4:
% obfs4 104.131.108.182:56880 EF577C30B9F788B0E1801CF7E433B3B77792B77A cert=0SFhfDQrKjUJP8Qq6wrwSICEPf3Vl/nJRsYxWbg3QRoSqhl2EB78MPS2lQxbXY4EW1wwXA iat-mode=0
% (nickname unknown):
% scramblesuit 188.226.213.208:54278 AA5A86C1490296EF4FACA946CC5A182FCD1C5B1E password=MD2VRP7WXAMSG7MKIGMHI4CB4BMSNO7T
This left enough bridges that participants in the later experiment would be able to connect
under the same circumstances as those in the earlier experiment.
We did not modify the set of bridges between the experiments,
with one exception.
One of the meek bridges changed its bridge identity fingerprint;
Tor clients check the identity fingerprint and refuse to connect
if it does not match.
Therefore we patched the correct fingerprint in the later experiment.

@@

\begin{table}
\centering
	\begin{tabular}{c r r r r }
	 & First & Proxy & Bridge & Summary \\
	\noalign{\hrule}
	All & 22\% & 57\% & 19\% & 2\% \\
	NEW & 40\% & 31\% & 19\% & 9\% \\ 
	OLD & 18\% & 63\% & 19\% & 0\% \\
	E1 & 45\% & 22\% & 32\% & 1\% \\
	E2 & 29\% & 48\% & 20\% & 2\% \\
	E3 & 19\% & 61\% & 18\% & 2\% \\
	\end{tabular}
\caption{active time} 
\label{table:active_time}
\end{table}

>>>>

@@

%\begin{table}
%\centering
%	\begin{tabular}{c r r r r }
%	 & First & Proxy & Bridge & Summary \\
%	\noalign{\hrule}
%	All & 22\% & 57\% & 19\% & 2\% \\
%	NEW & 40\% & 31\% & 19\% & 9\% \\ 
%	OLD & 18\% & 63\% & 19\% & 0\% \\
%	E1 & 45\% & 22\% & 32\% & 1\% \\
%	E2 & 29\% & 48\% & 20\% & 2\% \\
%	E3 & 19\% & 61\% & 18\% & 2\% \\
%	\end{tabular}
%\caption{active time} 
%\label{table:active_time}
%\end{table}
